---
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---

# Assessement    
  
1. True or False: The best way to keep your files organized for analysis is to indicate and set the working directory in each R script.

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE, eval=FALSE}
# New Analysis Script 
setwd("Desktop/CURE/Analysis/Data")
```

2. Fill in the operator used to create an object named "age" which contains the values 18, 19, 20, and 17:
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE, eval=FALSE}
age [_____] c(18, 19, 20, 17)
```

3. I have a vector that includes many different types of berries in a specific order (see below). How do I subset just "strawberries" from the object?
```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE, eval=FALSE}
berries <- c("strawberries", "blueberries", "raspberries", "blackberries", "cranberries")
```
A. <kbd>berries[1]</kbd>   
B. <kbd>berries(1)</kbd>  
C. <kbd>berries[,1]</kbd>  
D. <kbd>berries[c(2)]</kbd>  



4. After reading a data frame into R using the following code, I want to explore my data.    
<kbd>mydata <- read.csv("data/mydata.csv")</kbd>.      

Match the following functions with questions about the data: 
  
| Functions | Questions |
|-----|------|
| str(mydata) | What is the first row in my data frame? | 
| head(mydata) | What is the class of the row named row1? | 
| view(mydata) |  What are the first few rows in the data frame? |  
| mydata[,1] |  What is in the row named row1? |   
| "mydata$row1" |  What is the data frames structure?  |
| "class(mydata\$row1)" | What does my data frame look like? |    
   
     
     
5. **Activity**:    
Download specimen data for a species of interest using the iDigBio API in R following the steps learned in section 4. 
  a. What species did you download records for?
  b. How many observations were in this record set?
  c. Plot a map of these records and save this plot as a jpg. 



